Macro Impacts

### 2016-07-16 Macro Impacts Revised.tex
Realistic Stuff Beginning

%\pagebreak
%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
\end{document}

>>>>

\pagebreak
\section{Realistic Model}
Since I have realized that the curving of rays is non-negligible, Professor Tolley has suggested doing a realistic treatment of the problem. The displacement potential satisfies the inhomogeneous wave equation
\begin{align}
-\f{f}{\rho}&=v(r)^2\nabla^2\phi-\partial_t^2\phi\,,
\end{align}
where $v(r)=a^2-b^2r^2$. Note, $b$ is about 8 orders of magnitude smaller than a, so that the background varies slowly with respect to the frequency of the waves so the WKB approximation is appropriate. Denote 
\begin{align}
\hat L=v(r)^2\f{1}{r^2}\partial_r(r^2\partial_r)-\f{1}{r^2}(l(l+1))+\omega^2\,,
\end{align}
It is easy to see that $\hat L$ is Hermitian since it can be put in Sturm--Liouville form when stated as an eigenvalue problem
\begin{align}
-\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)+\f{r^2\omega^2-l(l+1)}{v(r)^2}}\phi=\lambda\phi\,.
\end{align}
Call the expression in the bracket on the left hand side $\hat L'$. We now impose finite boundary conditions, i.e. that the 0th and 1st derivatives of a solution vanish at $R_E$. Denote the eigenfunction corresponding to $\lambda$ as $\phi_\lambda$. Define the $L^2$ inner product
\begin{align}
\gen{f,g}=\int_0^{R_E}\diff r \f{v(r)^2}{r^2}\bar f(r)g(r)\,,
\end{align}
with respect to which $\hat L'$ is self-adjoint. We now employ the WKB ansatz (where $\delta\ll \f{a^2}{b^2R_E^2}$ *this is a guess - think about it!)
\begin{align}
\phi_\lambda(r)=\exp\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}(r)}\,,
\end{align}
and hence (note that $\delta$ is just an auxiliary variable that we will absorb into $S$ at the end of the calculation)
\begin{align}
\partial_r \phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}\phi_\lambda(r)\,,\\
&\sim\f1\delta S_{\lambda0}'(r)\phi_\lambda(r)\,,\\
\partial_r^2\phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}''(r)}\phi_\lambda(r)+\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}^2\phi_\lambda(r)\,,\\
&\sim\f1\delta S_{\lambda0}''(r)\phi_\lambda(r)+\f1{\delta^2}S_{\lambda0}'^2(r)\phi_\lambda(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)\phi_\lambda(r)\,.
\end{align}
Thus
\begin{align}
r^2\p{\f1\delta S_{\lambda0}''(r)+\f1{\delta^2}S_{\lambda0}'^2(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)}+2r\f1\delta S_{\lambda0}'(r)=-\f{r^2(\lambda-\omega^2)+l(l+1)}{v(r)^2}\,.
\end{align}
As we take $\delta$ to zero, the dominant balance is
\begin{align}
r^2 S'^2_{\lambda 0}(r)=-\f{r^2(\lambda-\omega^2)+l(l+1)}{v(r)^2}\,,
\end{align}
from which we obtain
\begin{align}
S_{\lambda 0}(r)=C_0\pm\I\f{\sqrt{(b^2l(l+1)+a^2(\lambda-\omega^2))v(r)}}{a^2b}\te{AppellF1}\ps{\f12,-\f12,1,\f32,\f{(\lambda-\omega^2)v(r)}{b^2l(l+1)+a^2(\lambda-\omega^2)},\f{v(r)}{a^2}}\,,
\end{align}
The first order contribution is then determined by
\begin{align}
S_{\lambda1}'(r)=-\f{1}{r}-\f{S_{\lambda0}''(r)}{2S_{\lambda0}'(r)}\,.
\end{align}
The solution is quite simple
\begin{align}
S_{\lambda1}(r)=C_1-\f14\ln\ps{\f{r^2\ps{l(l+1)+r^2(\lambda-\omega^2)}}{v(r)}}\,.
\end{align}
Hence, the eigenfunctions are, semiclassically
\begin{align}
\notag\phi_\lambda&=K_1\ps{\f{r^2\ps{l(l+1)+r^2(\lambda-\omega^2)}}{v(r)}}^{-1/4}e^{+\I\f{\sqrt{(b^2l(l+1)+a^2(\lambda-\omega^2))v(r)}}{a^2b}\te{AppellF1}\ps{\f12,-\f12,1,\f32,\f{(\lambda-\omega^2)v(r)}{b^2l(l+1)+a^2(\lambda-\omega^2)},\f{v(r)}{a^2}}}\\
&+K_2\ps{\f{r^2\ps{l(l+1)+r^2(\lambda-\omega^2)}}{v(r)}}^{-1/4}e^{-\I\f{\sqrt{(b^2l(l+1)+a^2(\lambda-\omega^2))v(r)}}{a^2b}\te{AppellF1}\ps{\f12,-\f12,1,\f32,\f{(\lambda-\omega^2)v(r)}{b^2l(l+1)+a^2(\lambda-\omega^2)},\f{v(r)}{a^2}}}\,.
\end{align}
Now we demand that $\phi$
\end{document}
